Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-09-25 manuscript/ERL_global_C_review.Rmd
drop some stats
#29

# records for excluded biome groupings ? 
n_records_BoB <- NA
n_records_Bomixed <- NA
n_records_Te_mixed <- NA

@@

For this analysis, we grouped forests into four broad biome types (tropical broadleaf, temperate broadleaf, temperate needleleaf, and boreal needleleaf) and two age classifications (young and mature). 
Climate zones (Fig. 1) were defined based on site geographic coordinates according to Köppen-Geiger zones (Rubel and Kottek 2010).
Tropical climates were defined to include all equatorial (A) zones, temperate climates were defined to include all warm temperate (C) zones and warmer snow climates (Dsa, Dsb, Dwa, Dwb, Dfa, and Dfb), and boreal climates were defined to include the colder snow climates (Dsc, Dsd, Dwc, Dwd, Dfc, and Dfd). 
Any forests in dry (B) and polar (E) Köppen-Geiger zones were excluded from the analysis. 
Leaf type (broadleaf / needleleaf) was defined based on descriptions in original publications (prioritized) or values extracted from a global map based on satellite observations [SYNMAP; @jung_exploiting_2006]. 
Forests were classified as “young” (< 100 years) or “mature” ($\ge$ 100 years or classified as “mature”, “old growth”, “intact”, or “undisturbed” in original publication). 
Assigning stands to these groupings required the exclusion of records for which ForC lacked records of stand age (n=`r round(n_records_age_unk/nrow(ForC_measurements)*100, digits=1)`% of records in full database), or geographic coordinates (n=`r round(n_sites_coord_unk/nrow(ForC_sites)*100, digits=1)`% of sites in full database). 
In total, our analysis retained `r round(n_records/n_focal_variable_records_eligible_for_inclusion*100, digits=1)` of the focal variable records for forests of known age. 
The most well-represented forest types excluded were boreal broadleaf (`r n_records_BoB` records) and boreal and temperate mixed broadleaf-needleleaf (`r n_records_Bomixed` and `r n_records_Te_mixed` records, respectively).

Data were analyzed to produce ...
*Schematics:* 
Data were summarized to produce schematics of C cycling across the eight biome - age group combinations identified above.
For mature forests, to obtain the values reported in the C cycle schematics, we first averaged any repeated measurements within a plot. 
Values were then averaged across plots clustered within 25 km of one another [*sensu* @anderson-teixeira_forc_2018], weighting by area sampled if available for all records. 
This step was taken to avoid pseudo-replication and to combine any records from sites with more than one name in ForC.

>>>>

@@

For this analysis, we grouped forests into four broad biome types (tropical broadleaf, temperate broadleaf, temperate needleleaf, and boreal needleleaf) and two age classifications (young and mature). 
Climate zones (Fig. 1) were defined based on site geographic coordinates according to Köppen-Geiger zones (Rubel and Kottek 2010).
Tropical climates were defined to include all equatorial (A) zones, temperate climates were defined to include all warm temperate (C) zones and warmer snow climates (Dsa, Dsb, Dwa, Dwb, Dfa, and Dfb), and boreal climates were defined to include the colder snow climates (Dsc, Dsd, Dwc, Dwd, Dfc, and Dfd). 
Any forests in dry (B) and polar (E) Köppen-Geiger zones were excluded from the analysis. 
Leaf type (broadleaf / needleleaf) was defined based on descriptions in original publications (prioritized) or values extracted from a global map based on satellite observations [SYNMAP; @jung_exploiting_2006]. 
Forests were classified as “young” (< 100 years) or “mature” ($\ge$ 100 years or classified as “mature”, “old growth”, “intact”, or “undisturbed” in original publication). 
Assigning stands to these groupings required the exclusion of records for which ForC lacked records of stand age (n=`r round(n_records_age_unk/nrow(ForC_measurements)*100, digits=1)`% of records in full database), or geographic coordinates (n=`r round(n_sites_coord_unk/nrow(ForC_sites)*100, digits=1)`% of sites in full database). 
In total, our analysis retained `r round(n_records/n_focal_variable_records_eligible_for_inclusion*100, digits=1)` of the focal variable records for forests of known age.

Data were analyzed to produce 
*Schematics:* 
Data were summarized to produce schematics of C cycling across the eight biome - age group combinations identified above.
For mature forests, to obtain the values reported in the C cycle schematics, we first averaged any repeated measurements within a plot. 
Values were then averaged across plots clustered within 25 km of one another [*sensu* @anderson-teixeira_forc_2018], weighting by area sampled if available for all records. 
This step was taken to avoid pseudo-replication and to combine any records from sites with more than one name in ForC.
